%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Samuel Preston}
\end{center}

\begin{center}
\small 07460945461 $|$
\href{mailto:samp.reston@outlook.com}{\underline{samp.reston@outlook.com}} $|$
\href{https://www.linkedin.com/in/samp-reston/}{\underline{linkedin.com/in/samp-reston}} 
\end{center}


%-----------Summary-----------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{Creative, diligent, and pioneering engineer looking for new challenges to solve. After 5+ years in the automotive sector working on in-house software, \textbf{saving £1 million per year}, I leveraged modern technologies and advancements as well as actively contributing back into the community. I secured a 2:1 at the \textbf{University of Warwick} while working full time at Jaguar Land Rover, while doing so I was ensuring the \textbf{latest standards} were being adhered to by implementing software configuration tracking across \textbf{£20+ million worth in assets}.}
  \resumeSubHeadingListEnd

%-----------Technical Experience-----------
\section{Technical Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jaguar Land Rover}{Jan 2021 - Present}
      {Framework Developer}{Warwickshire, UK}
      \resumeItemListStart
        \resumeItem{\textbf{Ideated, architected, and lead the development} of in-house software across multiple domains, taking direct customer feedback and iterating on the product. This required communications to \textbf{non-technical stakeholders} throughout the senior management for the local domain.}
        \resumeItem{Using the regulations for automotive diagnostics, I was able to develop internal tooling based around my own developed \textbf{open-source libraries}. This allowed for the implementation of parallel communication with embedded systems within vehicles with \textbf{Rust}, during which I utilised matrix CICD jobs to build the binary for multiple targets and publish these along with generated release notes.}
        \resumeItem{I have \textbf{pioneered} the use of the \textbf{Rust programming language} within JLR, assisting with those \textbf{junior and senior} to understand its benefits and where it can be most valuable within our toolchains. This has already led to the delivery of products of which are able to provide \textbf{£1 million} in savings per year.}
      \resumeItemListEnd
    \resumeSubheading
      {Jaguar Land Rover}{Sep 2018 -- Jan 2021}
      {Vehicle in the Loop Engineer}{Warwickshire, UK}
      \resumeItemListStart
        \resumeItem{\textbf{Lead the delivery} of new capabilities by interfacing with research centers such as \textbf{National Automotive Innovation Center} (NAIC) and JLR Whitley, to implement \textbf{electronics and microcontrollers}.}
        \resumeItem{Delivered crucial projects to \textbf{remotely control components} within the car to perform \textbf{end-to-end consumer faced testing}}
        \resumeItem{Supported the \textbf{rapid growth} of the team from 2 to 10 testing rigs, \textbf{increasing the testing capacity} of Level 5 in the loop rigs within the business. During this I also took ownership of the \textbf{maintenance and bug tracking} to ensure as the team scaled we didn't face unmaintainable systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% %-----------Interpersonal Skills-----------
% \section{Interpersonal Skills}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Communication, Training, and Coaching}{}
%       {Learning Development Network}{}
%       \resumeItemListStart
%       \resumeItem{Once built, my Rust project required communication to technical and non-technical leaders within this business.}
%       \resumeItem{}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd
%-----------Extracurricular-----------
\section{Extracurricular}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Open Source Contribution}{April 2024 - Present}
      {Rust - \href{https://crates.io/crates/doip-definitions}{\underline{DoIP Definitions}} - \href{https://crates.io/crates/doip-codec}{\underline{DoIP Codec}} - \href{https://github.com/rustfoundation/safety-critical-rust-consortium}{\underline{Safety Critical Rust Consortium}}}{}
      \resumeItemListStart
      \resumeItem{Develop and maintain libraries to support \textbf{automotive embedded development} with Rust. Utilising common and \textbf{best practices}, I was able to quickly gather \textbf{interest from others} to contribute towards a goal of combined specialisation.}
      \resumeItem{Supported JLR within the \textbf{Safety Critical Rust Consortium} to ensure JLR is aware of the progress made towards safety critical Rust, and assessing that JLR explores the latest technologies.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------Education-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Warwick}{Sep. 2020 - Jul. 2024}
      {2:1 BEng}{Applied Engineering - Product Creation}
      \resumeItemListStart
      \resumeItem{Demonstrated knowledge through research and presentation of product development utilising \textbf{quality assurance techniques} for varying levels of production.}
      \resumeItem{Generated from \textbf{functional requirements} a production system utilising PLCs and the OpenPLC editor software, including \textbf{flow control} considerations.}
      \resumeItem{Selectively enhanced my understanding of the \textbf{OSI model} through implementation of an office intranet and internet facilitation using \textbf{CISCO Packet Tracer}. This led to further understanding of Transport Protocol layers specifically TCP.}
      \resumeItemListEnd
    % \resumeSubheading
    %   {Coaching}{}
    %   {Learning Development Network}{}
    %   \resumeItemListStart
    %   \resumeItem{Demonstrated knowledge through research and presentation of product development utilising \textbf{quality assurance techniques} for varying levels of production.}
    %   \resumeItem{Generated from \textbf{functional requirements} a production system utilising PLCs and the OpenPLC editor software, including \textbf{flow control} considerations.}
    %   \resumeItem{Selectively enhanced my understanding of the \textbf{OSI model} through implementation of an office intranet and internet facilitation using \textbf{CISCO Packet Tracer}. This led to further understanding of Transport Protocol layers specifically TCP.}
    %   \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{document}