%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {}
    {Web Scraper} % Project
    {Birmingham, UK} % Location
    {Dec 2020 - Jul 2021} % Date(s)
    {
      \begin{cvitems}
        This web scraper started during the GPU shortages during 2020 and 2021, it was developed to notify those interested of availability of collectables and other desireable items. It was developed initially using Python and Selenium, but later after discussing with users, an interface was required. For this I developed an Electron application, which is where I first learnt ReactJS.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {}
    {European Amateur League} % Project
    {Birmingham, UK} % Location
    {Nov 2017 - Mar 2019} % Date(s)
    {
      \begin{cvitems}
        As Managing Director for European Amateur League I was responsible for the long term strategy of the organisation, including the development of new products, services, and managing the team of admins, broadcasters, and tournament staff. Ran up to 14 daily community matches, a monthly small tournament, and a quarterly major tournament with a prize pool. Achieved a total community of approx. 8000 users. Worked with a team of 15 volunteers to organise these events and moderation of the community. 
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
