\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Samuel Preston} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+44 794942 0516 \\ Birmingham, UK}
\address{\href{mailto:samp.reston@outlook.com}{samp.reston@outlook.com} \\ \href{https://www.linkedin.com/in/samp-reston/}{linkedin.com/in/samp-reston/} \\ \href{www.sampreston.co.uk}{www.sampreston.co.uk}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Web Developer with 2+ years of experience in web development, seeking full-time web development opportunities.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BEng, Applied Engineering}, University of Warwick \hfill {Expected 2024}\\
{\bf A-Levels, Maths, Further Maths, Physics}, Solihull Sixth Form \hfill {2017}\\

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & ReactJS, Next.js, TypeScript, MySQL, Git\\
Soft Skills & Agile Methodologies, Test Driven Development\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Framework Developer} \hfill Jan 2022 - Present\\
Jaguar Land Rover \hfill \textit{Gaydon, UK}
  \begin{itemize}
    \itemsep -3pt {}
      \item Developed a CI/CD pipeline and tool, leading to a 98.6\% decrease in software and configuration of £20m testing assets, enabling drastic increase in development and testing time.
      \item Led onboarding activities for new members of the team, including training and mentoring.
      \item Developing a tool for remote download of pre-production SW onto simulated and on-prem vehicles.
  \end{itemize}

\textbf{Web Developer} \hfill Dec 2020 - Present\\
Self Employed \hfill \textit{Remote, UK}
  \begin{itemize}
    \itemsep -3pt {}
      \item Designed and developed a fullstack web application using Next.js, TailwindCSS, and Google Maps.
      \item Worked with customer to increase SEO of their courses, resulting in a 21.5\% increase in conversion rates.
      \item Developed relationships with local businesses to understand their needs and develop solutions to problems.
  \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Freelancing} {Designed and then developed a personal portfolio using ReactJS, but later moved to Next.js to utilise server-side rendering.}
\item \textbf{Web Scraper} {This web scraper started during the GPU shortages during 2020 and 2021, it was developed to notify those interested of availability of collectables and other desireable items. It was developed initially using Python and Selenium, but later after discussing with users, an interface was required. For this I developed an Electron application, which is where I first learnt ReactJS.}
\item \textbf{European Amateur League} {Ran up to 14 daily community matches, a monthly small tournament, and a quarterly major tournament with a prize pool. Achieved a total community of approx. 8000 users. Worked with a team of 15 volunteers to organise these events and moderation of the community.}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities}
\begin{itemize}
    \item Explore new technologies in the web development space. I attend as many technology related events I can and have written tutorial-style blog posts related to how to use a new technology, library, or framework.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership}
\begin{itemize}
    \item As Managing Director for European Amateur League I was responsible for the long term strategy of the organisation, including the development of new products, services, and managing the team of admins, broadcasters, and tournament staff.
\end{itemize}


\end{rSection}


\end{document}
